Precision calculations for cosmic shear

### 2017-02-08 cfhtlens.tex
Moved Fig 2 into the applcation to CFHTLenS section Included definition of xi+ Big changes in purple please check and remove purple when you're happy

\ch{In this work, we focus on the weak-lensing power spectrum projection, and
assess the impact of various approximations on cosmological constraints from
CFHTLenS. We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, which is
given by}
\begin{equation}
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\end{equation}
\ch{where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum through equation~\ref{eq:P_ell_limber1} when adopting a first-order extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting a second-order extended Limber approximation \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}.  Note that as we have shown in section~\ref{sec:comp} that the second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection, we do not investigate predictions for the two-point shear correlation function using the full spherical projection.  This is because on a sphere,
correlation functions cannot be related to the power spectrum by a Hankel transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.}

>>>>

\ch{In this work, we focus on the weak-lensing power spectrum projection, and
assess the impact of various approximations on cosmological constraints from
CFHTLenS. We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, which is
given by}
\begin{equation}
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\end{equation}
\ch{where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum through equation~\ref{eq:P_ell_limber1} when adopting a first-order extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting a second-order extended Limber approximation \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}.  }

\ch{On a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform in equation~\ref{eqn:xiGG}, as the power spectrum is not defined for non-integer $\ell$ \citep[see][for alternative spherical-sky formulae for the two-point correlation function]{2005PhRvD..72b3516C}.  As we have shown in section~\ref{sec:comp} that the spherical second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection for $\ell > 3$, we do not present predictions for the two-point shear correlation function using the full spherical projection, instead choosing the spherical second-order extended Limber approximation (Ext2Sph) as our `truth' in this case.}

\ch{Figure.~\ref{fig:xi_pm_K16} presents the two-point correlation functions $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear power spectrum listed in Table~\ref{tab:cases}. The adopted CFHTLenS redshift distribution and fiducial cosmological model are the same as in Figure.~\ref{fig:Cl_cases}.   }

\begin{figure}

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_comp}
      \includegraphics{figures/xi_m_comp}
    }

    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_delta}
      \includegraphics{figures/xi_m_delta}
    }
  \end{center}

  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
    The lower panels shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
    Limber.}
    \ch{ExtL2Fl isn't in the table - so yes agreed to remove that from both plots}
    \ch{I'd keep the ExtL1Fl, just incase someone is daft enough to do that approximation one day.}
    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.
  }

  \label{fig:xi_pm_K16}

\end{figure}

### 2017-02-08 limber2.tex
Moved Fig 2 into the applcation to CFHTLenS section Included definition of xi+ Big changes in purple please check and remove purple when you're happy

  \caption{Shear power spectrum for different approximation. Limber to first order: standard with flat-sky (L1Fl),
        extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
        and extended in the spherical expansion (ExtL1Sph);
        second-order Limber approximations: extended flat sky (ExtL2Fl), extended hybrid flat sky (ExtL2FlHyb),
        and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
        The left panels show the total power spectrum.
        See Table \ref{tab:cases} for more details on the different approximations.
        }

@@

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@

In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
for the shear power spectrum. The redshift distribution and cosmological model are the same 
as in Fig.~\ref{fig:Cl_cases}.

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_comp}
      \includegraphics{figures/xi_m_comp}
    }

    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_delta}
      \includegraphics{figures/xi_m_delta}
    }
  \end{center}

  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
    Limber.}
    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.
  }

  \label{fig:xi_pm_K16}

>>>>

  \caption{Shear power spectrum for different approximation. Limber to first order: standard with flat-sky (L1Fl),
        extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
        and extended in the spherical expansion (ExtL1Sph);
        second-order Limber approximations: extended flat sky (ExtL2Fl), extended hybrid flat sky (ExtL2FlHyb),
        and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
        The left panels show the total power spectrum.
        See Table \ref{tab:cases} for more details on the different approximations.     
       \ch{ExtL2Fl isn't in the table - so suggest to remove that from both plots}
        }

@@

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
    & \ch{I think this should be 1?}%$\ellbar^2(\ell, 2)/(\ell+1/2)^4$ 
    & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@
